\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-22 tex/paper.tex
Added abstract and clarified load test

%}}}
\begin{abstract}
    \fix Abstract is written last

\keywords{}
\end{abstract}

@@

\subsubsection{Run-time Complexity of Operations}
\begin{figure}[H] 
    \centering{
         \begin{tikzpicture}[nodes={draw, circle, fill=blue!20}, <-]
             \node{R}
             child{node{C} child{node{C}} child{node{C} child{node{M}} child{node{M}}}}
             child{node{C}};
         \end{tikzpicture}
    }
    \caption{Project Tree\\R - RootContainer, C - Container, M - Content}
    \label{fig:project_tree}
\end{figure}

@@

After adding indices, the building of the project tree was able to finish 50 times faster and the
server was able to serve 2100 requests/s, see Listing~\ref{INDEXREQUEST}.

>>>>

%}}}
\begin{abstract}
This work presents a technique for incorporating Copy-on-Write in the development of a high level
system on top of an unaware persistent storage. The system in this case is a security management
system, but the technique and conclusions drawn are general enough to be applicable to any system
with vaguely similar consistency requirements. The scalability of the system is tested and the
technique is evaluated and the technique is shown to be very efficient (scalable to >
simultaneous users on a single node), but a better solution is also suggested in the
conclusion.\\

\keywords{CDN, Copy-on-Write, Eventual Consistency, MongoDB, Persistent Storage, Scalability, 
Software Security}
\end{abstract}

@@

\subsubsection{Run-time Complexity of Operations}
The runtime complexities of the operations in this section are quite intuitive, that is why they 
are only explained, and not proven to fulfil the complexities which are claimed. 
%To prove them, methods like the master theorem~\cite{ALGORITHMS} or \dots could be used.

\begin{figure}[H] 
    \centering{
         \begin{tikzpicture}[nodes={draw, circle, fill=blue!20}, <-]
             \node{R}
             child{node{C} child{node{C}} child{node{C} child{node{M}} child{node{M}}}}
             child{node{C}};
         \end{tikzpicture}
    }
    \caption{Project Tree\\R - RootContainer, C - Container, M - Content}
    \label{fig:project_tree}
\end{figure}

@@

After adding indices, the building of the project tree was able to finish 50 times faster and the
server was able to serve 2100 requests/s, see Listing~\ref{INDEXREQUEST}. If using the same
approximated average that was used in connection to Listing~\ref{TREEREQUEST} (30 requests/s), the
maximum number of clients that one node can handle will be >60000, without taking the web servers
limits or content posting into consideration.
